Adaptive Algorithms Employing Continuous Linear Functionals

### 2018-08-03 AutoAlgorithmLinearFunctionalDataVerC.tex
Updates from ShareLaTeX

Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution to some error tolerance for all inputs in $\ch$:
\begin{multline} \label{adapErrCrit}
\ca(\ch) : = \left\{ \text{algorithms } A:\ch \times (0,\infty) \rightarrow \cg : 
\right . \\ \left .
\bignorm[\cg]{S(f) - A(f,\varepsilon)} \le \varepsilon \ \forall f \in \ch, \ \varepsilon > 0 
\right \}.
\end{multline}
Algorithms in $\ca(\ch)$ are allowed to sample adaptively any bounded, linear functionals
of the input function $f$.  They must require only a finite number of linear functionals for each input function and positive tolerance.  The definition of $\ch$ can be used in constructing algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.  Following \cite{KunEtal19a}

>>>>

Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution to some error tolerance for all inputs in $\ch$:
\begin{multline} \label{adapErrCrit}
\ca(\ch) : = \left\{ \text{algorithms } A:\ch \times (0,\infty) \rightarrow \cg : 
\right . \\ \left .
\bignorm[\cg]{S(f) - A(f,\varepsilon)} \le \varepsilon \ \forall f \in \ch, \ \varepsilon > 0 
\right \}.
\end{multline}
Algorithms in $\ca(\ch)$ are allowed to sample adaptively any bounded, linear functionals
of the input function $f$.  They must require only a finite number of linear functionals for each input function and positive tolerance.  The definition of $\ch$ can be used in constructing algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.  Following \cite{KunEtal19a} we call a problem \emph{solvable} for inputs $\ch$ if $\ca(\ch)$ is non-empty.

Note that our problem is not solvable for $\cf$.  This can be proven by contradiction. We show that there is some function, $f \in \cf$, that looks like the zero function, but whose corresponding solution, $S(f)$, is far from $0$.   Choose any $A \in \ca(\cf)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$. Since only a finite number of samples is used, there exists some nonzero $f \in \cf$ that  appears exactly like $0$ to the algorithm, but which has a non-zero solution, $S(f)$. This means that $L_1(f) = \cdots = L_n(f) = 0$, and so $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.  Since our algorithm successfully produces an approximation with error no greater than $\varepsilon$,
\begin{align*}
    \varepsilon &\ge \frac 12 \left[ \norm[\cg]{S(0) - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(cf,\varepsilon)}\right] \\
    & =  \frac 12 \left[ \norm[\cg]{0 - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(0,\varepsilon)}\right] \\
    & \ge  \frac {\abs{c}\norm[\cg]{S(f)}}2  \qquad \text{by the triangle inequality}.
\end{align*}
Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.  Thus, $\ca(\cf)$ is empty, and our problem is not solvable for $\cf$.  However, it is solvable for well-chosen subsets of $\cf$.
